---
title: "getabstract"
output: html_notebook
---
Test bed for DOIs

```{r}
url<-"https://doi.org/10.1007/s10530-012-0332-8";test<-getabstract(url);print(test)


newurl <- readLines(curl::curl(as.character(httr::GET(doi)[1])))[15]
test<-gsub("%3A",":",gsub("%2F","/",newurl))
doi<-gsub('^.*direct=\\s*|\\s*%3Fvia.*$', '', test)

```


Properly functioning dois:

doi: 10.1186/2047-2382-2-19
type: Four subsections (background, methods, results, conclusions)
journal: Environmental Evidence
publisher: BioMedCentral

doi: 10.1007/s10530-012-0332-8
type: single block of text
journal: Biological Invasions
publisher: Springer

doi: 10.1007/s13280-016-0773-x
type: short abstract followed by "Introduction"
journal: AMBIO
publisher: Spriner

doi: 10.1002/aqc.2225
type: numbered list abstract
journal: Aquatic Conservation - Marine and Freshwater Ecosystems
publisher: Wiley

doi: 10.1139/cjfas-2016-0261
type: block abstract followed by references (subscription journal)
journal: Canadian Journal of Fisheries and Aquatic Sciences
publisher: Canadian Science Publishing

doi: 10.1017/S0030605313000811
type: no abstract availabe - publisher response stating this
journal: Oryx
publisher: Cambridge University Press

doi: 10.1007/s40362-014-0023-1
type: abstract not followed by regular subtitle
journal: Springer Systematic Reviews
publisher: Springer




Problems requiring resolution:

doi: 10.1016/j.jclinepi.2017.08.010
type: doi links to blank page (referral to publisher site)
journal: Journal of Clinical Epidemiology
publisher: Elsevier
solution: text <- httr::GET("http://doi.org/10.1016/j.jclinepi.2017.08.010");text[1] (only gets the intermediate link). https://github.com/yusuzech/r-web-scraping-cheat-sheet/blob/master/README.md#rvest3

```{r}
doi<-"https://doi.org/10.1016/j.envint.2015.07.011"
newurl <- readLines(curl::curl(as.character(httr::GET(doi)[1])))[15]
test<-gsub("%3A",":",gsub("%2F","/",newurl))
doi<-gsub('^.*direct=\\s*|\\s*%3Fvia.*$', '', test)
```

doi: 10.3354/meps09978
type: abstract denoted by "ABSTRACT: " inline with text, followed by "KEY WORDS: ", pulling back non-abstract text (keywords, copyright statement, citation links, etc.)
journal: Marine Ecology Progress Series
publisher: Inter-Research Science Publisher
solution: 

doi: 10.1002/ece3.1722
type: short abstract not followed by "Introduction", "Background", "References" or "This is a preview of subscription content"
journal: Ecology and Evolution
publisher: Wiley
solution: if lines[abstract+1] is NOT a subsection (i.e. less than c.8 words) AND lines[abstract+3] IS a subsection, then return lines[abstract+1]

doi: 10.1111/cobi.12449
type: no abstract (commentary)
journal: Conservation Biology
publisher: Wiley
solution: return error - "No abstract available"

doi: 10.1016/j.envint.2015.07.011
type: doi links to blank page (referral to publisher site)
journal: Environment International
publisher: Elsevier
solution: see above

doi: 10.1038/s41559-018-0502-x
type: abstract is a brief paragraph in bold above the main text
journal: Nature Ecology & Evolution
publisher: Nature
solution: extract first paragraph where the word "abstract" is missing

doi: 10.1016/j.earscirev.2017.12.015
type: doi links to blank page (referral to publisher site)
journal: Earth-Science Reviews
publisher: Elsevier
solution: see above

doi: 10.1038/s41558-018-0180-3
type: abstract is a brief paragraph in bold above the main text
journal: Nature Climate Change
publisher: Nature
solution: extract first paragraph where the word "abstract" is missing
